---
title: "Homework-2"
output: 
  pdf_document: default
  html_document: default
date: "4th Oct 2020"
theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,cache=TRUE,eval = FALSE)
library(ggplot2)
```



```{r}
newyork_zipcode<-read.csv('CovidData-NYCZipcodeCounts.csv',header=T)
newyork_state<-read.csv('CovidData-NYStateDailyCounts.csv',header=T)

```

### 1(a) A bar graph showing the number of zipcodes in each NYC borough

```{r, fig.width=6, fig.height=4}
library(ggplot2)
ggplot(data=newyork_zipcode,mapping= aes(x=BOROUGH_GROUP)) + geom_bar() + labs(x=" ", y="Number of zip codes")

```

### 1(b)Histogram of the number of Covid deaths by zipcode, using a bin width of 20:

```{r}
ggplot(data=newyork_zipcode) + geom_histogram(mapping=aes(x=COVID_DEATH_COUNT),binwidth=20,color="grey")
```


### 1(c)Similar to a histogram of the number of Covid deaths by zipcode, using a bin width of 20, but with the bars joined by lines instead:

```{r}
ggplot(data=newyork_zipcode,aes(x=COVID_DEATH_COUNT)) + geom_freqpoly(binwidth=20)
```

### 1(d)Side-by-side boxplots of the percent tested positive in each zipcode:

```{r}
ggplot(data=newyork_zipcode,aes(x=BOROUGH_GROUP,y=PERCENT_POSITIVE)) + geom_boxplot()
```

### 1(e)Scatter plot of Covid deaths by zipcode vs Covid cases by zipcode:

```{r}
ggplot(data=newyork_zipcode,aes(x=COVID_CASE_COUNT,y=COVID_DEATH_COUNT)) + geom_point(aes(color=BOROUGH_GROUP,size=BOROUGH_GROUP))
```

### 1(f)Scatter  plot  of  zipcode  deaths  vs  percent  positive,  separated  by  borough  and  with  afitted line:

```{r}
ggplot(data=newyork_zipcode,aes(x=PERCENT_POSITIVE,y=COVID_DEATH_COUNT)) + geom_point() + geom_smooth(method = "lm") + facet_grid(rows=vars(BOROUGH_GROUP))
```

### 1(g)A timeplot of the daily number of cases and number of hospitalizations:


```{r}
ggplot(data=newyork_state) + geom_point(aes(x= as.numeric(row.names(newyork_state)),y=Cases,group=1)) + geom_line(aes(x=as.numeric(row.names(newyork_state)),y=Hospitalizations,group=1),color="grey") + labs(x = "Day 1 is Feb 29,2020", y = "Number of Cases and Hospitalizations") 
```

### 1(h)Scatter plot of the daily number of deaths vs daily number of hospitalizations:

```{r}
ggplot(data=newyork_state,aes(x=Hospitalizations,y=Deaths)) + geom_point(aes(color=Cases),shape=4)
```

### 1(i)Scatter plot of the daily proportion of deaths to hospitalizatons vs number of hospitalizations:
```{r}
newyork_state$proportion<-(newyork_state$Deaths/newyork_state$Hospitalizations)

ggplot(data=newyork_state,aes(x=Hospitalizations,y=proportion)) + geom_point(aes(color=Cases),na.rm=TRUE) + labs(y="Proportion of death to hospitalizations")
```



### Q2(a)Find the total number of cases in New York City.Find also the total population

```{r}
total_num_of_cases<-sum(newyork_zipcode$COVID_CASE_COUNT)
paste( "There are total",total_num_of_cases,"cases")
```

### There are Total  207461 cases

```{r}
total_population<-sum(newyork_zipcode$POP_DENOMINATOR)

paste("The total populations is",total_population)
```

### The total populations is 8394354.96

### Q2(b)Obtain summary statistics of all the numerical columns inCovidbyzip.  Use the lapply and sapply functions.

```{r}
lapply(newyork_zipcode[,c(4:10)],summary)

sapply(newyork_zipcode[,c(4:10)],summary)
```

### Q2(c) Obtain summary statistics of Covid case counts for Brooklyn zipcodes only.

```{r}
summary(newyork_zipcode[newyork_zipcode$BOROUGH_GROUP=="Brooklyn","COVID_CASE_COUNT"])
```

### Q2(d)Do the same thing for the Bronx zipcodes only and Staten Island zipcodes only.

```{r}
summary(newyork_zipcode[newyork_zipcode$BOROUGH_GROUP=="Bronx","COVID_CASE_COUNT"])

summary(newyork_zipcode[newyork_zipcode$BOROUGH_GROUP=="Staten Island","COVID_CASE_COUNT"])

```
### Q2(e)Identify the NYC zipcode and neighborhood name with the highest percent positive.

```{r}
newyork_zipcode[newyork_zipcode$PERCENT_POSITIVE==max(newyork_zipcode$PERCENT_POSITIVE),c(1,2)]

paste("The zipcode is 11369 and neighborhood name=Airport/East Elmhurst")

```

## The zipcode is 11369 and neighborhood name=Airport/East Elmhurst"

### Q2(f) On which day were there the most number of hospitalizations relative to cases in NYState?

```{r, echo=FALSE}
library(sqldf)
library(lubridate)

sqldf("select DATE_OF_INTEREST,MAX(Hospitalizations) from newyork_state")

wday("04/06/2020",label=TRUE)

paste("The date is 04/06/2020 and day is Sunday")

```

## The date is 04/06/2020 and day is Sunday

### Q3(a)Use seq to create a vector with elements 1,3, 5, ...  to 27.  Extract the 10th value of this vector.

```{r}
vec<-seq(1,27,2)

vec[10]
```
### Q3(b)Reverse the order of your vector above.

```{r}
rev(vec)
```

### Q3(c) Create a vector consisting of, thirty 1’s, twenty 6’s and eleven 9’s.

```{r}
vec3<-rep(c(1,6,9),c(30,20,11))

vec3

```

### Q3(d)Create  a  diagonal  matrix  with  the  numbers  2,  4,  6,  ...   20  in  the  diagonal.Find  its inverse.

```{r}
vec4<-seq(2,20,by=2)

vec4

diag_mat<-diag(vec4)


solve(diag_mat)

```

### Q3(e) Extract the 7th column of the matrix you created in 3(d).  Make this vector (i.e the 7thcolumn) into a 2×5 matrix, fillng out the matrix by column.

```{r}
new_mat<-matrix(diag_mat[,7],nrow=2, ncol=5,byrow=FALSE)

new_mat
```

