---
title: 'Homework-4'
output:
  pdf_document: default
  html_document: default
date: 9 Nov, 2020
theme: cerulean
---

<!-- For more info on RMarkdown see http://rmarkdown.rstudio.com/ -->


  
### Q1Write a function to evaluate ab given a and b. The function should have a default value of 3 for b.
  
```{r}

f1<-function(a,b=3){
  a^b
}

f1(2)
```


### Q2 Write a function that accepts two arguments, an integer and a vector, and returns TRUE if the integer is inside the vector

```{r}
f2<-function(x,y) {
  for (a in y){
    if (a==x){
      return(TRUE)
    }
  }
  return(FALSE)
}

f2(5,c(2,3,4,5,5))
```


### Q3 Write a function that, given an integer and a vector, will return the number of times the integer occurs in the vector.

```{r}
f3<-function(a,b){
  count=0
  for (i in b) {
    if (i==a){
    count<- count + 1
    }
  }
  return(count)
}

f3(a=5,b=c(3,4,5,5))

```


### Q4.Use the mtcars dataset for this question. Use one of the apply functions to and the mean of every column in mtcars.

```{r}
data(mtcars)
sapply(mtcars,mean)
```


### Q5.Write a function in R that takes as input a non-negative integer n and returns Fn. Use a for loop in the function. Then use the function to find F20 and F100.

```{r}
f5<-function(a){
  old_sum = 0
  new_sum = 1
  if(a==0){
    return(old_sum)
  }else if(a==1){
    return(new_sum)
  }else{
  for (i in 2:a){
    temp_sum = new_sum
    new_sum = new_sum + old_sum
    old_sum = temp_sum
  }
    return(new_sum)
  }
  
}

f5(20)
f5(100)
```

### Q6.Write an R function to compute fn(x) for any real number x and positive integer n. Use a while loop to do this. The function should return a vector with two numbers, the value of fn(x) and the approximation error exp fn(x). Run your function for x = 3; n = 10 and x = 4; n = 3.

```{r}
f6<-function(x,n){
  taylor=0
  c=0
  while(c<=n){
    taylor=taylor + (x^c)/factorial(c)
    c<-c+1
  }
  return(c(taylor,exp(x)-taylor))
}

f6(3,10)
f6(4,3)

```


### Q7.Write two R functions to compute the factorial of any user-supplied positive integer n. The first function should calculate (and return) n! using a for loop. The second function calculates and returns n! recursively.

```{r}
f7<-function(n){
  factorial=1
  for (i in seq_len(n)){
    factorial=factorial * i
  }
  factorial
}

f7(5)
```

```{r}
recursive<-function(n){
  if (n==1 || n==0){
    1}else{
      recursive(n-1)*n
    }
}

recursive(5)
```


### Q8.Write a function that accepts a vector of numbers (of length >= 3) and returns a vector of moving averages, i.e. with x = (x1; : : : ; xn), the output is a vector with the values.


```{r}
f8<-function(x){
  if (length(x)>=3){
    d<-0
    vector<-c()
    for (i in 1:length(x)-2){
      d<-(x[i] +x[i+1] + x[i+2])/3
      vector<-c(vector,d)
    }
  }
  vector
}

f8(x=c(1,2,3,4,5,6,7,8))

```

### Q9.Write a function that accepts a vector of numbers and returns the values of the function f(x) evaluated at that vector of numbers. Make a plot of this function for 2<=x<=3.


```{r}
f9<-function(x){
   value=c()
   for (i in x){
     if (i<0){
     val=i^2 + 2*i + 3
     value<-c(value,val)
   }else if(0<=i && i<2){
     val=i+3
     value<-c(value,val)
   }else{
     val= i^2 + 4*i -7
     value<-c(value,val)
   }
   } 
    plot(value)
   return(value)
}

f9(c(-2,-1,0,1,2,3)) 
```



### Q10

```{r warning = FALSE}
set.seed(20330)
mydata <- rgamma(100, shape=4, scale=5)


make.NegLogLik <- function(data, fixed=c(FALSE, FALSE)){
  params <- fixed
  function(param.values){
    params[!fixed] <- param.values
    a <- params[1]
    b <- params[2]
    value <- (a-1)* sum(log(data)) -length(data) * log(gamma(a)) -(length(data) * a) * log(b) - (1/b) * sum(data)
    value
  }
}

my.negloglik <- make.NegLogLik(mydata)
```

```{r warning = FALSE}
optim(c(a=2,b=2), my.negloglik)$par
```
